---
title: "Getting Started with PlayerDataR"
author: "PlayerData"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with PlayerDataR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE  # Set to TRUE to run code chunks
)
```

# Introduction

PlayerDataR is an R wrapper for making GraphQL requests with OAuth 2 authentication. This vignette will guide you through the basics of using the package.

## Installation

First, install the package and its dependencies:

```{r install}
# Install dependencies
install.packages(c("ghql", "httr", "jsonlite"))

# For authorization code flow (optional but recommended)
install.packages("httpuv")
```

## Loading the Package

```{r load}
library(playerdatar)
```

## OAuth Authentication

PlayerDataR supports two OAuth 2 grant types:

### Client Credentials Flow (Default)

This is the simplest flow, suitable for server-to-server communication:

```{r client-credentials}
client <- create_gql_client(
  client_id = "your-client-id",
  client_secret = "your-client-secret",
  grant_type = "client_credentials"
)
```

### Authorization Code Flow

This flow requires user interaction through a browser:

```{r auth-code}
client <- create_gql_client(
  client_id = "your-client-id",
  client_secret = "your-client-secret",
  grant_type = "authorization_code"
)
```

When using the authorization code flow, a browser window will open for authentication.

## Executing Queries

### Simple Query

```{r simple-query}
query <- '{
  sports {
    id
    name
    isIndoor
  }
}'

result <- execute_query(client, query)
print(result)
```

### Query with Variables

```{r query-variables}
query <- 'query GetSessions($clubId: ID!) {
  sessions(filter: { clubIdEq: $clubId }) {
    id
    startTime
    endTime
  }
}'

variables <- list(clubId = "your-club-id")
result <- execute_query(
  client, 
  query, 
  query_name = "GetSessions",
  variables = variables
)
```

## Executing Mutations

```{r mutation-update-session}
mutation <- '
mutation UpdateSession($id: ID!, $attributes: SessionAttributesInput!) {
  updateSession(id: $id, attributes: $attributes) {
    errors {
      fullMessages
    }
    session {
      startTime
    }
  }
}
'

result <- execute_mutation(
  client,
  mutation,
  mutation_name = "UpdateSession",
  variables = list(
    id = "your-session-id",
    attributes = list(startTime = "2026-01-01T17:59:00.000Z") # ISO 8601 format
  )
)
```

## Token Management

The package automatically handles token refresh. If you need to manually refresh a token:

```{r refresh-token}
refresh_client_token(client)
```

Tokens are cached in a file (default: `.token`) to avoid unnecessary authentication requests.

## Custom Configuration

You can customize the GraphQL endpoint and OAuth URLs:

```{r custom-config}
client <- create_gql_client(
  client_id = "your-client-id",
  client_secret = "your-client-secret",
  url = "https://app.playerdata.co.uk/api/graphql",
  token_url = "https://app.playerdata.co.uk/oauth/token",
  authorize_url = "https://app.playerdata.co.uk/oauth/authorize",
  token_file = ".token",
  port = 8080
)
```

## Next Steps

- See `?create_gql_client` for all available options
- Check `?execute_query` and `?execute_mutation` for detailed function documentation
- Review the example script in `example.r` for more examples
